
```{css, echo=FALSE}
/* Style for the main tabs */
.nav-tabs > li > a {
  background-color: #A3C4E5; 
  color: #5F5B57; 
}

/* Style for the active main tab */
.nav-tabs > li.active > a {
  background-color: #4276AA; 
  color: #ffffff; 
}

/* Style for the sub-tabs */
.tab-content .tab-pane .nav > li > a {
  background-color: #D2D2D2; 
  color: #3E3D3D; 
}

/* Style for the active sub-tab */
.tab-content .tab-pane .nav > li.active > a {
  background-color: #6D6D6D; 
  color: #ffffff; 
}
```

```{r}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readxl)
library(rvest)
library(plotly)
library(knitr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(survival)
library(kableExtra)
library(purrr)
library(tableone)
library(skimr)
```
```


# Data

_Source, scraping method, cleaning, etc._

## Data Import

Click `show` on the right to view the code chunk for data importing.
```{r message = FALSE}
lowbirthweight <- read_csv("csv_NYC_lowbirthweight.csv")
pm2_5 <- read_csv("pm2.5.csv")
edu_NY <- read_excel("Edu_NY.xlsx")
race_NY <- read_excel("Race_NY.xlsx")
HHincome_NY <- read_excel("HHincome_NY.xlsx")
Age_NY <- read_excel("Age_NY.xlsx")
Sex_NY <- read_excel("Sex_NY.xlsx")
health <- read_excel("chir_current_data.xlsx")
uscounties <- read_csv("uscounties.csv") #Simplemaps.com
```

9 data files are obtained from publicly available sources online. These will be imported, wrangled properly, and merged to create a complete data for further analysis.

## Data Wrangling {.tabset .tabset-fade}

Click `show` on the right to view the code chunk for data importing.


### PM2.5 Dataset  
```{r warning=FALSE}
pm2_5 <- pm2_5 %>% 
  janitor::clean_names()%>%
  select (county,value) %>%
  rename (annual_pm2.5 = "value")

pm2_5 %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
The dataset is obtained from EPH Tracking Website from CDC (https://ephtracking.cdc.gov/DataExplorer/). This has `r nrow(pm2_5)` rows and `r ncol(pm2_5)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `annual_pm2.5`: annual estimated PM2.5 concentration at each county (ug/m^3)

### Demographic Dataset {.tabset .tabset-fade}

The following set of demographic datasets is obtained from Census Reporter webpage (https://censusreporter.org/).

#### Education Attainment
```{r, warning=FALSE}
edu <- edu_NY %>% 
  janitor::clean_names()%>%
  mutate (percentage_high_education = (bach_male+master_male+prof_male+doct_male+bach_female+master_female+prof_female+doct_female)/total) %>%
  filter(str_detect (name, " County, NY")) %>% 
  mutate(county = str_replace (name, " County, NY", "")) %>%
  select(county,percentage_high_education) %>%
  mutate(county = str_replace (county, "St.", "St")) %>%
  mutate(county = str_replace (county, "Stuben", "Steuben"))%>%
  select(county,percentage_high_education)

edu %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```  
This has `r nrow(edu)` rows and `r ncol(edu)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `percentage_high_education`: percentage of population who finished a higher education level (higher than a bachelor degree)

#### Ethnicity
```{r warning=FALSE}  
race_non_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_white") %>% 
  select (county,percent_non_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_non_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_black") %>% 
  select (county,percent_non_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_white") %>% 
  select (county,percent_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_black") %>% 
  select (county,percent_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_merge <- race_non_hisp_white %>%
  inner_join(race_non_hisp_black, by = "county") %>%
  inner_join(race_hisp_white, by = "county") %>%
  inner_join(race_hisp_black, by = "county")

race_merge <- race_merge %>% 
  mutate (percent_other = 1 - percent_non_hisp_white - percent_non_hisp_black - percent_hisp_white - percent_hisp_black)

race_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
This has `r nrow(race_merge)` rows and `r ncol(race_merge)` columns of data. In which, 6 variables are:  
  - `county`: NY county name   
  - `percent_non_hisp_white`: percentage of population who are identified as Non-Hispanic White  
  - `percent_non_hisp_black`: percentage of population who are identified as Non-Hispanic Black    
  - `percent_hisp_white`: percentage of population who are identified as Hispanic White  
  - `percent_hisp_black`: percentage of population who are identified as Hispanic Black  
  - `percent_other`: percentage of population who are identified as any other ethinic groups    


#### Household Income
```{r warning=FALSE}
income <- HHincome_NY %>%
  janitor::clean_names() %>% 
  filter (x1 == "percent_high_income") %>%
   pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_high_income") %>%
  select (county,percent_high_income) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_high_income ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
This has `r nrow(income)` rows and `r ncol(income)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `percent_high_income`: percentage of population who are at higher income households (>$75,000 annually)

#### Median Age
```{r warning=FALSE}
age <- Age_NY %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "median_age") %>%
  select (county,median_age) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,median_age ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

age %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
This has `r nrow(age)` rows and `r ncol(age)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `median_age`: median age of the population at each county  

#### Sex
```{r warning=FALSE}
sex <- Sex_NY %>% 
  janitor::clean_names() %>% 
  filter (x1 == "Male:") %>%
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_male") %>%
  select (county,percent_male) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_male ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

sex%>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
This has `r nrow(sex)` rows and `r ncol(sex)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `percent_male`: percentage of population who are identified as male  

#### Low Birthweight Data 
```{r warning=FALSE}
lowbirthweight <- lowbirthweight %>% 
  janitor::clean_names()%>%
  select (region_county, percentage)%>%
  rename (county = "region_county", percent_lowbirthweight = "percentage") 

lowbirthweight %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
This has `r nrow(lowbirthweight)` rows and `r ncol(lowbirthweight)` columns of data. In which, 2 variables are:  
  - `county`: NY county name   
  - `percent_lowbirthweight`: percentage of children being born being identified as low birth weight (<2,500g) (https://www.health.ny.gov/)

#### Health Indicator Dataset 
The following dataset is obtained from New York State Department of Health (https://www.health.ny.gov/) that contains 4 different health indicators that will complement with the low birthweight. These 5 will act as our outcomes of interest for our regression models.

```{r warning=FALSE}
health <- health %>%
  janitor::clean_names()%>%
  select (geographic_area,indicator_title,topic_area,rate_percent,measurement) %>%
  filter( str_detect (geographic_area, " County")) %>% 
  mutate (county = str_replace (geographic_area, " County", "")) %>%
  select (county, everything()) %>%
  select (-geographic_area) %>%
  filter(topic_area == "Cancer Indicators" | topic_area == "Respiratory Disease Indicators" | topic_area == "Cardiovascular Disease Indicators" | topic_area == "Maternal and Infant Health Indicators")
  
cancer <- health %>% 
  filter (topic_area == "Cancer Indicators") %>% 
  filter (indicator_title == "All cancer incidence rate per 100,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>%
  mutate(rate_percent = as.numeric(rate_percent)/10) %>%
  rename (cancer_mortality_per_10k = "rate_percent")

resp <- health %>%
  filter (topic_area == "Respiratory Disease Indicators") %>%
  filter (indicator_title == "Asthma hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (asthma_hosp_rate_per_10k = "rate_percent")

cardio <- health %>%
  filter (topic_area == "Cardiovascular Disease Indicators") %>%
  filter (indicator_title == "Cardiovascular disease hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (cardio_hosp_rate_per_10k = "rate_percent")

maternal <- health %>%
  filter (topic_area == "Maternal and Infant Health Indicators") %>%
  filter (indicator_title == "Percentage of premature births with <37 weeks gestation") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (premature_percentage = "rate_percent")
health_merge <- maternal %>% 
  inner_join(cancer, by = "county") %>%
  inner_join(resp, by = "county") %>% 
  inner_join(cardio, by = "county") 

health_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```
They are:   
  - `cancer_mortality_per_10k`: percentage of cancer mortality per 100 thousands people in each NY county (Cancer Indicator)    
  - `asthma_hosp_rate_per_10k`: percentage of asthma hospitalization per 10 thousands people in each NY county (Respiratory Disease Indicator)     
  - `cardio_hosp_rate_per_10k`": percentage of cardiovascular-disease-related hospitalization per 10 thousands people in each NY county (Cardiovascular Disease Indicator)   
  - `premature_percentage`: percentage of children being born prematurely (<37  gestational weeks) in each NY county

### Merge dataset
Here we perform `inner_join()` to create 1 bigger dataset called `demographic_merge`. Then, we join them with our `lowbirthweight` & `pm2_5` to make a finalized data frame called `merge`. And, we will use this for regression model. 

```{r warning=FALSE}

demographic_merge <- age %>%
  inner_join(sex,  by = "county") %>%
  inner_join(income, by = "county") %>% 
  inner_join(race_merge, by = "county") %>% 
  inner_join(edu, by = "county") %>%
  mutate(county = str_replace (county, "St ", "St. "))
  

merge <- lowbirthweight %>% 
  inner_join(pm2_5, by = "county") %>%
  inner_join(health_merge, by = "county") %>% 
  inner_join(demographic_merge, by = "county") 

merge <- merge %>% 
  select (county, annual_pm2.5,everything())%>%
  mutate(asthma_hosp_rate_per_10k = as.numeric(asthma_hosp_rate_per_10k))%>%
  mutate(cardio_hosp_rate_per_10k = as.numeric(cardio_hosp_rate_per_10k)) %>%
  mutate(premature_percentage = as.numeric(premature_percentage))%>%
  mutate(cancer_mortality_per_10k = as.numeric(cancer_mortality_per_10k))

merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")
```

This `merge` dataset is comprised of `r nrow(merge)` rows and `r ncol(merge)` columns of data, with first column being the name of the `county`, and other 15 beings all continuous variables of identified indicators of the whole 62 counties of NY state.  



### Making Map File
```{r warning=FALSE}
uscounties <- uscounties %>% 
  filter (state_id == "NY") %>%
  select (county, lat, lng)

map <- merge %>% 
  inner_join(uscounties, by ="county")

write.csv(map, "NY_map.csv", row.names = FALSE)

```
This file is specifically made for the purpose of making map (in Shiny App). We obtained latitude and longitude data of all NY counties from SimpleMaps Database (https://simplemaps.com/data/us-counties).

