

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(readxl)
library(rvest)
library(plotly)
library(knitr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
lowbirthweight <- read_csv("csv_NYC_lowbirthweight.csv")
pm2_5 <- read_csv("pm2.5.csv")
edu_NY <- read_excel("Edu_NY.xlsx")
race_NY <- read_excel("Race_NY.xlsx")
HHincome_NY <- read_excel("HHincome_NY.xlsx")
Age_NY <- read_excel("Age_NY.xlsx")
Sex_NY <- read_excel("Sex_NY.xlsx")
health <- read_excel("chir_current_data.xlsx")
uscounties <- read_csv("uscounties.csv") #Simplemaps.com

pm2_5 <- pm2_5 %>% 
  janitor::clean_names()%>%
  select (county,value) %>%
  rename (annual_pm2.5 = "value")

edu <- edu_NY %>% 
  janitor::clean_names()%>%
  mutate (percentage_high_education = (bach_male+master_male+prof_male+doct_male+bach_female+master_female+prof_female+doct_female)/total) %>%
  filter(str_detect (name, " County, NY")) %>% 
  mutate(county = str_replace (name, " County, NY", "")) %>%
  select(county,percentage_high_education) %>%
  mutate(county = str_replace (county, "St.", "St")) %>%
  mutate(county = str_replace (county, "Stuben", "Steuben"))%>%
  select(county,percentage_high_education)

race_non_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_white") %>% 
  select (county,percent_non_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_non_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_black") %>% 
  select (county,percent_non_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_white") %>% 
  select (county,percent_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_black") %>% 
  select (county,percent_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_merge <- race_non_hisp_white %>%
  inner_join(race_non_hisp_black, by = "county") %>%
  inner_join(race_hisp_white, by = "county") %>%
  inner_join(race_hisp_black, by = "county")

race_merge <- race_merge %>% 
  mutate (percent_other = 1 - percent_non_hisp_white - percent_non_hisp_black - percent_hisp_white - percent_hisp_black)

income <- HHincome_NY %>%
  janitor::clean_names() %>% 
  filter (x1 == "percent_high_income") %>%
   pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_high_income") %>%
  select (county,percent_high_income) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_high_income ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

age <- Age_NY %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "median_age") %>%
  select (county,median_age) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,median_age ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

sex <- Sex_NY %>% 
  janitor::clean_names() %>% 
  filter (x1 == "Male:") %>%
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_male") %>%
  select (county,percent_male) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_male ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

lowbirthweight <- lowbirthweight %>% 
  janitor::clean_names()%>%
  select (region_county, percentage)%>%
  rename (county = "region_county", percent_lowbirthweight = "percentage") 

health <- health %>%
  janitor::clean_names()%>%
  select (geographic_area,indicator_title,topic_area,rate_percent,measurement) %>%
  filter( str_detect (geographic_area, " County")) %>% 
  mutate (county = str_replace (geographic_area, " County", "")) %>%
  select (county, everything()) %>%
  select (-geographic_area) %>%
  filter(topic_area == "Cancer Indicators" | topic_area == "Respiratory Disease Indicators" | topic_area == "Cardiovascular Disease Indicators" | topic_area == "Maternal and Infant Health Indicators")
  
cancer <- health %>% 
  filter (topic_area == "Cancer Indicators") %>% 
  filter (indicator_title == "All cancer incidence rate per 100,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (cancer_mortality_per_100k = "rate_percent")

resp <- health %>%
  filter (topic_area == "Respiratory Disease Indicators") %>%
  filter (indicator_title == "Asthma hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (asthma_hosp_rate_per_10k = "rate_percent")

cardio <- health %>%
  filter (topic_area == "Cardiovascular Disease Indicators") %>%
  filter (indicator_title == "Cardiovascular disease hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (cardio_hosp_rate_per_10k = "rate_percent")

maternal <- health %>%
  filter (topic_area == "Maternal and Infant Health Indicators") %>%
  filter (indicator_title == "Percentage of premature births with <37 weeks gestation") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (premature_percentage = "rate_percent")

health_merge <- maternal %>% 
  inner_join(cancer, by = "county") %>%
  inner_join(resp, by = "county") %>% 
  inner_join(cardio, by = "county") 

demographic_merge <- age %>%
  inner_join(sex,  by = "county") %>%
  inner_join(income, by = "county") %>% 
  inner_join(race_merge, by = "county") %>% 
  inner_join(edu, by = "county") %>%
  mutate(county = str_replace (county, "St ", "St. "))
  

merge <- lowbirthweight %>% 
  inner_join(pm2_5, by = "county") %>%
  inner_join(health_merge, by = "county") %>% 
  inner_join(demographic_merge, by = "county") 

merge <- merge %>% 
  select (county, annual_pm2.5,everything())%>%
  mutate(asthma_hosp_rate_per_10k = as.numeric(asthma_hosp_rate_per_10k))%>%
  mutate(cardio_hosp_rate_per_10k = as.numeric(cardio_hosp_rate_per_10k)) %>%
  mutate(premature_percentage = as.numeric(premature_percentage))%>%
  mutate(cancer_mortality_per_100k = as.numeric(cancer_mortality_per_100k))


uscounties <- uscounties %>% 
  filter (state_id == "NY") %>%
  select (county, lat, lng)

map <- merge %>% 
  inner_join(uscounties, by ="county")

write.csv(map, "NY_map.csv", row.names = FALSE)
```  

# Exploratory Analysis

_Visualizations, summaries, and exploratory statistical analyses. Justify the steps you took, and show any major changes to your ideas._

###### Percentage of High Income
```{r}
merge %>%
 plot_ly(
    x = ~reorder(county, percent_high_income),
    y = ~percent_high_income,
    type = "bar",
    marker = list(color = "red1")
  ) %>%
  layout(
    title = "Percentage of High Income",
    xaxis = list(title = "County Name", categoryorder = "total descending"),
    yaxis = list(title = "Percentage"),
    barmode = "stack"
  )
```

###### Racial Composition 
```{r}
race_plot <- merge %>% 
  select (county, percent_non_hisp_white, percent_non_hisp_black, percent_hisp_white, percent_hisp_black, percent_other) %>%
  pivot_longer(
    cols = starts_with("percent_"), names_to = "race", values_to = "percentage") 

race_plot%>%
  plot_ly(x = ~county, y = ~percentage, type = "bar",color = ~race,colors = "RdYlGn", hoverinfo = "y+name") %>% 
  layout(barmode = "stack",
         title = "Racial Composition in NY county",
         xaxis = list(title = "County"),
         yaxis = list(title = "Percentage (%)"))
```

##### Outcome Graphs 

###### Low birthweight Rate 
```{r}
merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~percent_lowbirthweight,
    color = ~county,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Low Birthweight",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Percentage of Low Birthweight"),
    showlegend = FALSE
  )
```

###### Premature Birth 
```{r}
merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~premature_percentage,
    color = ~county,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Premature Birth",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate of Premature Birth"),
    showlegend = FALSE
  )
```


###### Asthma Hospitalization 
```{r}
merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~asthma_hosp_rate_per_10k,
    color = ~county,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Asthma Hospitalization",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 10k"),
    showlegend = FALSE
  )
```

###### Cancer Mortality Rate 
```{r}
merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~cancer_mortality_per_100k,
    color = ~county,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Cancer Mortality",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 100k"),
    showlegend = FALSE
  )
```

###### Cardiovascular Rate 
```{r}
merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~cardio_hosp_rate_per_10k,
    color = ~county,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Cardiovascular Disease Hospitalization",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 10k"),
    showlegend = FALSE
  )
```

# Additional analysis

_If you undertake formal statistical analyses, describe these in detail_

##### Linear regression pm2.5 concentration and percentage of low birth weight  

```{r}
lm_pm2.5_birthweight <- lm(percent_lowbirthweight~annual_pm2.5 , data=merge)
summary(lm_pm2.5_birthweight)

lm_pm2.5_birthweight_adjusted <-lm(percent_lowbirthweight ~ annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percentage_high_education + percent_male, data=merge)
summary(lm_pm2.5_birthweight_adjusted)

```

##### stepwise 
```{r}
step(lm_pm2.5_birthweight_adjusted, direction = 'both')

lm_pm2.5_birthweight_adjusted_best <- lm(percent_lowbirthweight~median_age + percent_non_hisp_black, data=merge)

summary (lm_pm2.5_birthweight_adjusted_best) %>%
  tab_model()

```

##### Linear regression pm2.5 concentration and premature birth
```{r}
lm_pm2.5_premature <- lm(premature_percentage ~ annual_pm2.5 , data=merge)
summary(lm_pm2.5_premature)

lm_pm2.5_premature_adjusted <-lm(premature_percentage ~ annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percentage_high_education + percent_male, data=merge)
summary(lm_pm2.5_premature_adjusted)
```

##### stepwise 
```{r}
step(lm_pm2.5_premature_adjusted, direction = 'both')

lm_pm2.5_premature_adjusted_best <- lm(premature_percentage ~ median_age + percent_non_hisp_black, data = merge)
summary(lm_pm2.5_premature_adjusted_best)%>%
  tab_model()
```

##### Linear regression pm2.5 concentration and cancer mortality
```{r}
lm_pm2.5_cancer <- lm(cancer_mortality_per_100k ~ annual_pm2.5 , data=merge)
summary(lm_pm2.5_cancer)

lm_pm2.5_cancer_adjusted <-lm(cancer_mortality_per_100k ~annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percentage_high_education + percent_male, data=merge)
summary(lm_pm2.5_cancer_adjusted)
```

##### stepwise 
```{r}
step(lm_pm2.5_cancer_adjusted, direction = 'both')

lm_pm2.5_cancer_adjusted_best <- lm(cancer_mortality_per_100k ~ annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percent_male, data =merge)
summary (lm_pm2.5_cancer_adjusted_best)%>%
  tab_model()
```

##### Linear regression pm2.5 concentration and asthma hospitalization 
```{r}
lm_pm2.5_asthma <- lm(asthma_hosp_rate_per_10k ~ annual_pm2.5 , data=merge)
summary(lm_pm2.5_asthma)

lm_pm2.5_asthma_adjusted <-lm(asthma_hosp_rate_per_10k ~ annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percentage_high_education + percent_male, data=merge)
summary(lm_pm2.5_asthma_adjusted)
```

##### stepwise 
```{r}
step(lm_pm2.5_asthma_adjusted, direction = 'both')

lm_pm2.5_asthma_adjusted_best <- lm(asthma_hosp_rate_per_10k~ percent_high_income + percent_non_hisp_black + percent_hisp_black + percentage_high_education, data=merge)
summary(lm_pm2.5_asthma_adjusted_best)%>%
  tab_model()
```

##### Linear regression pm2.5 concentration and cardiovascular disease hospitalization
```{r}
lm_pm2.5_cardio <- lm(cardio_hosp_rate_per_10k ~ annual_pm2.5 , data=merge)
summary(lm_pm2.5_cardio)

lm_pm2.5_cardio_adjusted <-lm(cardio_hosp_rate_per_10k ~annual_pm2.5 + median_age + percent_high_income + percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percent_hisp_black + percentage_high_education + percent_male, data=merge)
summary(lm_pm2.5_cardio_adjusted)
```

##### stepwise 
```{r}
step(lm_pm2.5_cardio_adjusted, direction = 'both')

lm_pm2.5_cardio_adjusted_best <-lm(cardio_hosp_rate_per_10k ~annual_pm2.5 + median_age +percent_non_hisp_white + percent_non_hisp_black + percent_hisp_white + percentage_high_education + percent_male, data=merge)
summary (lm_pm2.5_cardio_adjusted_best)%>%
  tab_model()
```

#### All models together 
```{r}
tab_model(lm_pm2.5_birthweight_adjusted_best,lm_pm2.5_premature_adjusted_best,lm_pm2.5_cancer_adjusted_best,lm_pm2.5_asthma_adjusted_best,lm_pm2.5_cardio_adjusted )
```
