
```{css, echo=FALSE}
/* Style for the main tabs */
.nav-tabs > li > a {
  background-color: #A3C4E5; 
  color: #5F5B57; 
}

/* Style for the active main tab */
.nav-tabs > li.active > a {
  background-color: #4276AA; 
  color: #ffffff; 
}

/* Style for the sub-tabs */
.tab-content .tab-pane .nav > li > a {
  background-color: #D2D2D2; 
  color: #3E3D3D; 
}

/* Style for the active sub-tab */
.tab-content .tab-pane .nav > li.active > a {
  background-color: #6D6D6D; 
  color: #ffffff; 
}
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readxl)
library(rvest)
library(plotly)
library(knitr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(survival)
library(kableExtra)
library(purrr)
library(tableone)
library(skimr)

lowbirthweight <- read_csv("csv_NYC_lowbirthweight.csv")
pm2_5 <- read_csv("pm2.5.csv")
edu_NY <- read_excel("Edu_NY.xlsx")
race_NY <- read_excel("Race_NY.xlsx")
HHincome_NY <- read_excel("HHincome_NY.xlsx")
Age_NY <- read_excel("Age_NY.xlsx")
Sex_NY <- read_excel("Sex_NY.xlsx")
health <- read_excel("chir_current_data.xlsx")
uscounties <- read_csv("uscounties.csv") #Simplemaps.com

pm2_5 <- pm2_5 %>% 
  janitor::clean_names()%>%
  select (county,value) %>%
  rename (annual_pm2.5 = "value")

pm2_5 %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

edu <- edu_NY %>% 
  janitor::clean_names()%>%
  mutate (percentage_high_education = (bach_male+master_male+prof_male+doct_male+bach_female+master_female+prof_female+doct_female)/total) %>%
  filter(str_detect (name, " County, NY")) %>% 
  mutate(county = str_replace (name, " County, NY", "")) %>%
  select(county,percentage_high_education) %>%
  mutate(county = str_replace (county, "St.", "St")) %>%
  mutate(county = str_replace (county, "Stuben", "Steuben"))%>%
  select(county,percentage_high_education)

edu %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

race_non_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_white") %>% 
  select (county,percent_non_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_non_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Non-Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_non_hisp_black") %>% 
  select (county,percent_non_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_non_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_white <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "White Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_white") %>% 
  select (county,percent_hisp_white) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_white ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_hisp_black <- race_NY %>% 
  janitor::clean_names()%>%
  filter( x1 == "Black Hispanic") %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_hisp_black") %>% 
  select (county,percent_hisp_black) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_hisp_black ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_merge <- race_non_hisp_white %>%
  inner_join(race_non_hisp_black, by = "county") %>%
  inner_join(race_hisp_white, by = "county") %>%
  inner_join(race_hisp_black, by = "county")

race_merge <- race_merge %>% 
  mutate (percent_other = 1 - percent_non_hisp_white - percent_non_hisp_black - percent_hisp_white - percent_hisp_black)

race_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

income <- HHincome_NY %>%
  janitor::clean_names() %>% 
  filter (x1 == "percent_high_income") %>%
   pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_high_income") %>%
  select (county,percent_high_income) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_high_income ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

race_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

age <- Age_NY %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "median_age") %>%
  select (county,median_age) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,median_age ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

age %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

sex <- Sex_NY %>% 
  janitor::clean_names() %>% 
  filter (x1 == "Male:") %>%
  pivot_longer(
    albany_county_ny : yates_county_ny,
    names_to = "county",
    values_to = "percent_male") %>%
  select (county,percent_male) %>%
  separate(county, into = c("county", "x"), sep = "_county_") %>%
  select (county,percent_male ) %>%
  mutate(county = str_replace (county, "_", " ")) %>%
  mutate_at(vars(county), str_to_title)

sex%>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

lowbirthweight <- lowbirthweight %>% 
  janitor::clean_names()%>%
  select (region_county, percentage)%>%
  rename (county = "region_county", percent_lowbirthweight = "percentage") 

lowbirthweight %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

health <- health %>%
  janitor::clean_names()%>%
  select (geographic_area,indicator_title,topic_area,rate_percent,measurement) %>%
  filter( str_detect (geographic_area, " County")) %>% 
  mutate (county = str_replace (geographic_area, " County", "")) %>%
  select (county, everything()) %>%
  select (-geographic_area) %>%
  filter(topic_area == "Cancer Indicators" | topic_area == "Respiratory Disease Indicators" | topic_area == "Cardiovascular Disease Indicators" | topic_area == "Maternal and Infant Health Indicators")
  
cancer <- health %>% 
  filter (topic_area == "Cancer Indicators") %>% 
  filter (indicator_title == "All cancer incidence rate per 100,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>%
  mutate(rate_percent = as.numeric(rate_percent)/10) %>%
  rename (cancer_mortality_per_10k = "rate_percent")

resp <- health %>%
  filter (topic_area == "Respiratory Disease Indicators") %>%
  filter (indicator_title == "Asthma hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (asthma_hosp_rate_per_10k = "rate_percent")

cardio <- health %>%
  filter (topic_area == "Cardiovascular Disease Indicators") %>%
  filter (indicator_title == "Cardiovascular disease hospitalization rate per 10,000") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (cardio_hosp_rate_per_10k = "rate_percent")

maternal <- health %>%
  filter (topic_area == "Maternal and Infant Health Indicators") %>%
  filter (indicator_title == "Percentage of premature births with <37 weeks gestation") %>% 
  select (-c(indicator_title, topic_area, measurement)) %>% 
  rename (premature_percentage = "rate_percent")
health_merge <- maternal %>% 
  inner_join(cancer, by = "county") %>%
  inner_join(resp, by = "county") %>% 
  inner_join(cardio, by = "county") 

health_merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

demographic_merge <- age %>%
  inner_join(sex,  by = "county") %>%
  inner_join(income, by = "county") %>% 
  inner_join(race_merge, by = "county") %>% 
  inner_join(edu, by = "county") %>%
  mutate(county = str_replace (county, "St ", "St. "))
  

merge <- lowbirthweight %>% 
  inner_join(pm2_5, by = "county") %>%
  inner_join(health_merge, by = "county") %>% 
  inner_join(demographic_merge, by = "county") 

merge <- merge %>% 
  select (county, annual_pm2.5,everything())%>%
  mutate(asthma_hosp_rate_per_10k = as.numeric(asthma_hosp_rate_per_10k))%>%
  mutate(cardio_hosp_rate_per_10k = as.numeric(cardio_hosp_rate_per_10k)) %>%
  mutate(premature_percentage = as.numeric(premature_percentage))%>%
  mutate(cancer_mortality_per_10k = as.numeric(cancer_mortality_per_10k))

merge %>% 
  knitr::kable(digits = 3) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), font_size = 12) %>% 
  kableExtra::scroll_box(width = "100%", height = "300px")

uscounties <- uscounties %>% 
  filter (state_id == "NY") %>%
  select (county, lat, lng)

map <- merge %>% 
  inner_join(uscounties, by ="county")

write.csv(map, "NY_map.csv", row.names = FALSE)
```  

# EDA {.tabset .tabset-fade}

_Visualizations, summaries, and exploratory statistical analyses. Justify the steps you took, and show any major changes to your ideas._


## Descriptive Summary

First, we want to understand all the chosen variables we have. Since they are all continuous, we want to look at how many data points are being missing, their mean, median, and standard deviation. The code chunk below summarizes all of that statistics from our `merge` dataset.

```{r, warning=FALSE}
merge_cont =
  merge %>% 
  select(-county)

skim_table <- skim(merge_cont)
numeric_summary <- skim_table %>%
  select(Variables = skim_variable, Nmiss = n_missing, Mean = numeric.mean, Median = numeric.p50, STD = numeric.sd)


kable(numeric_summary, "html", digits = 1) %>%
  kable_styling(full_width = FALSE, position = "center", font_size = 13) %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "3cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "2cm")

```

The table provides descriptive statistics for various variables in the dataset. Key insights include the average `annual_pm2.5` level being 7.0, with a small standard deviation of 1.1, indicating relatively consistent air quality. Additionally, variables such as `premature_percentage` and `cancer_mortality_per_10k` show slight variability with a small number of missing values, while hospitalization rates and demographic characteristics exhibit diverse distributions. Overall, the summary highlights the central tendency, variability, and distribution characteristics of the dataset's variables.


## Percentage of High Income
Hover over the interactive graph or zoom in for more detailed information. 

Then, we aimed to look that the distribution of `percent_high_income` across all counties. We performed a general barplot that allowed us to understand the overall distribution.

```{r warning=FALSE}
merge %>%
 plot_ly(
    x = ~reorder(county, percent_high_income),
    y = ~percent_high_income,
    type = "bar",
    marker = list(color = "red1")
  ) %>%
  layout(
    title = "Percentage of High Income",
    xaxis = list(title = "County Name", categoryorder = "total descending"),
    yaxis = list(title = "Percentage"),
    barmode = "stack"
  )
```

The bar chart depicts the "Percentage of High Income" across 62 counties of New York State, ordered from the highest to the lowest percentage. Nassau county has the highest percentage of household with an annual income of more than $75,000 (categorized as high income), while that of the Bronx county is the lowest.

## Racial Composition 
Hover over the interactive graph or zoom in for more detailed information. 

Due to the nature of variety of racial group indicators of each county, we wanted to make a stacked bargraph to see the different between each county's racial composition.

```{r warning=FALSE}
race_plot <- merge %>% 
  select (county, percent_non_hisp_white, percent_non_hisp_black, percent_hisp_white, percent_hisp_black, percent_other) %>%
  pivot_longer(
    cols = starts_with("percent_"), names_to = "race", values_to = "percentage") 

race_plot%>%
  plot_ly(x = ~county, y = ~percentage, type = "bar",color = ~race,colors = "RdYlGn", hoverinfo = "y+name") %>% 
  layout(barmode = "stack",
         title = "Racial Composition in NY county",
         xaxis = list(title = "County"),
         yaxis = list(title = "Percentage (%)"))
```

This stacked bar chart displays the racial demographics across 62 New York counties. Each bar represents a county and is divided into segments that reflect the percentage of the county's population of the following racial categories: non-Hispanic White, non-Hispanic Black, Hispanic White, Hispanic Black, and Other. The majority of New York State population is non-Hispanic-White, which is also the major racial group in almost all counties, except in Bronx county and Queens county. 

## 5 Outcome Graphs {.tabset .tabset-fade}
The prevalence of our 5 outcomes of interest across 62 counties are illustrated in these 5 graphs below. For each outcome, we have highlighted the TOP 5 to be circled with <span style="color:red;"> red color</span>, while the bottom 5 will be circled with <span style="color:blue;"> blue color</span>, for easier understanding as there are many data points for NY State.

### Low birthweight Rate 
Hover over the interactive graph or zoom in for more detailed information. 

```{r warning=FALSE}
# Create a scatter plot
LBR_graph <- merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~percent_lowbirthweight,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Low Birthweight",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Percentage of Low Birthweight"),
    showlegend = FALSE
  )

# Identify the top and bottom points
top_points <- merge %>% arrange(desc(percent_lowbirthweight)) %>% slice_head(n = 5)
bottom_points <- merge %>% arrange(percent_lowbirthweight) %>% slice_head(n = 5)

# Identify the other points
suppressMessages({other_points <- merge %>%
  anti_join(top_points) %>%
  anti_join(bottom_points)})

# Add markers for the top and bottom points
LBR_graph <- LBR_graph %>%
  add_markers(
    data = top_points,
    x = ~county,
    y = ~percent_lowbirthweight,
    color = I("red"),  # Customize color for top points
    size = I(10),      # Customize marker size for top points
    name = "Top 5"
  ) %>%
  add_markers(
    data = bottom_points,
    x = ~county,
    y = ~percent_lowbirthweight,
    color = I("blue"),  # Customize color for bottom points
    size = I(10),       # Customize marker size for bottom points
    name = "Bottom 5") %>%
  add_markers(
    data = other_points,
    x = ~county,
    y = ~percent_lowbirthweight,
    color = I("grey"),  # Customize color for other points
    size = I(5),        # Customize marker size for other points
    name = "Other Points"
  )

# Display the plot
LBR_graph

```

TOP 5: <span style="color:red;"> (Bronx, 10.2), (Schenectady, 9.2), (Monroe, 9.1), (Fulton, 8.8), (Erie, 8.8) </span>.

BOTTOM 5: <span style="color:blue;"> (Hamilton,0), (Schuyler,2.8), (Yates, 4), (Schoharie, 5.1), (Rockland, 5.6)</span>.  

### Premature Birth 
Hover over the interactive graph or zoom in for more detailed information. 

```{r warning=FALSE}
# Create a scatter plot
premature_graph <- merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~premature_percentage,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Premature Birth",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Percentage of Premature Birth"),
    showlegend = FALSE
  )

# Identify the top and bottom points
top_points1 <- merge %>% arrange(desc(premature_percentage)) %>% slice_head(n = 5)
bottom_points1 <- merge %>% arrange(premature_percentage) %>% slice_head(n = 5)

# Identify the other points
suppressMessages({other_points1 <- merge %>%
  anti_join(top_points1) %>%
  anti_join(bottom_points1)})

# Add markers for the top and bottom points
premature_graph <- premature_graph %>%
  add_markers(
    data = top_points1,
    x = ~county,
    y = ~premature_percentage,
    color = I("red"),  # Customize color for top points
    size = I(10),      # Customize marker size for top points
    name = "Top 5"
  ) %>%
  add_markers(
    data = bottom_points1,
    x = ~county,
    y = ~premature_percentage,
    color = I("blue"),  # Customize color for bottom points
    size = I(10),       # Customize marker size for bottom points
    name = "Bottom 5") %>%
  add_markers(
    data = other_points1,
    x = ~county,
    y = ~premature_percentage,
    color = I("grey"),  # Customize color for other points
    size = I(5),        # Customize marker size for other points
    name = "Other Points"
  )

# Display the plot
premature_graph
```

TOP 5: <span style="color:red;"> (Washington, 11.1), (Schenectady, 10.3), (Bronx, 10.3), (Sullivan, 10.3), (Wyoming, 10.3) </span>.

BOTTOM 5: <span style="color:blue;"> (Schuyler,5.2), (Yates , 6), (Rockland, 6.3), (Tompskin, 6.5), (Lewis, 7)</span>.    

### Asthma Hospitalization 
Hover over the interactive graph or zoom in for more detailed information. 

```{r warning=FALSE}
# Create a scatter plot
asthma_graph <- merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~asthma_hosp_rate_per_10k,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Asthma Hospitalization",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 10k"),
    showlegend = FALSE
  )

# Identify the top and bottom points
top_points2 <- merge %>% arrange(desc(asthma_hosp_rate_per_10k)) %>% slice_head(n = 5)
bottom_points2 <- merge %>% arrange(asthma_hosp_rate_per_10k) %>% slice_head(n = 5)

# Identify the other points
suppressMessages({other_points2 <- merge %>%
  anti_join(top_points2) %>%
  anti_join(bottom_points2)})

# Add markers for the top and bottom points
asthma_graph <- asthma_graph %>%
  add_markers(
    data = top_points2,
    x = ~county,
    y = ~asthma_hosp_rate_per_10k,
    color = I("red"),  # Customize color for top points
    size = I(10),      # Customize marker size for top points
    name = "Top 5"
  ) %>%
  add_markers(
    data = bottom_points2,
    x = ~county,
    y = ~asthma_hosp_rate_per_10k,
    color = I("blue"),  # Customize color for bottom points
    size = I(10),       # Customize marker size for bottom points
    name = "Bottom 5") %>%
  add_markers(
    data = other_points2,
    x = ~county,
    y = ~asthma_hosp_rate_per_10k,
    color = I("grey"),  # Customize color for other points
    size = I(5),        # Customize marker size for other points
    name = "Other Points"
  )

# Display the plot
asthma_graph
```

TOP 5: <span style="color:red;"> (Bronx, 28.4), (Kings, 10.7), (New York, 8.4), (Richmond, 7.9), (Queens, 7.8) </span>.

BOTTOM 5: <span style="color:blue;"> (Orleans,1.6), (Seneca , 1.7), (Tompskin, 1.7), (Fulton, 1.7), (Madison, 1.8)</span>. 

### Cancer Mortality Rate 
Hover over the interactive graph or zoom in for more detailed information. 

```{r warning=FALSE}
# Create a scatter plot
cancer_graph <- merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~cancer_mortality_per_10k,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Cancer Mortality",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 10k"),
    showlegend = FALSE
  )

# Identify the top and bottom points
top_points3 <- merge %>% arrange(desc(cancer_mortality_per_10k)) %>% slice_head(n = 5)
bottom_points3 <- merge %>% arrange(cancer_mortality_per_10k) %>% slice_head(n = 5)

# Identify the other points
suppressMessages({other_points3 <- merge %>%
  anti_join(top_points3) %>%
  anti_join(bottom_points3)})

# Add markers for the top and bottom points
cancer_graph <- cancer_graph %>%
  add_markers(
    data = top_points3,
    x = ~county,
    y = ~cancer_mortality_per_10k,
    color = I("red"),  # Customize color for top points
    size = I(10),      # Customize marker size for top points
    name = "Top 5"
  ) %>%
  add_markers(
    data = bottom_points3,
    x = ~county,
    y = ~cancer_mortality_per_10k,
    color = I("blue"),  # Customize color for bottom points
    size = I(10),       # Customize marker size for bottom points
    name = "Bottom 5") %>%
  add_markers(
    data = other_points3,
    x = ~county,
    y = ~cancer_mortality_per_10k,
    color = I("grey"),  # Customize color for other points
    size = I(5),        # Customize marker size for other points
    name = "Other Points"
  )

# Display the plot
cancer_graph
```


TOP 5: <span style="color:red;"> (Columbia, 82.23), (Warren, 80.66), (Greene, 79.08), (Niagara, 78.86),  (Schuyler, 77.66) </span>.

BOTTOM 5: <span style="color:blue;"> (Bronx ,45.87), (Kings , 47.96), (Tompskin, 49.56), (Queens, 51.6), (Orange, 53.48) </span>. 


### Cardiovascular Rate 
Hover over the interactive graph or zoom in for more detailed information. 

```{r warning=FALSE}

# Create a scatter plot
cardio_graph <- merge %>%
  drop_na() %>%
  plot_ly(
    x = ~county,
    y = ~cardio_hosp_rate_per_10k,
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    title = "Rate of Cardiovascular Disease Hospitalization",
    xaxis = list(title = "County", tickangle = 90),
    yaxis = list(title = "Rate per 10k"),
    showlegend = FALSE
  )

# Identify the top and bottom points
top_points4 <- merge %>% arrange(desc(cardio_hosp_rate_per_10k)) %>% slice_head(n = 5)
bottom_points4 <- merge %>% arrange(cardio_hosp_rate_per_10k) %>% slice_head(n = 5)

# Identify the other points
suppressMessages({other_points4 <- merge %>%
  anti_join(top_points4) %>%
  anti_join(bottom_points4)})

# Add markers for the top and bottom points
cardio_graph <- cardio_graph %>%
  add_markers(
    data = top_points4,
    x = ~county,
    y = ~cardio_hosp_rate_per_10k,
    color = I("red"),  # Customize color for top points
    size = I(10),      # Customize marker size for top points
    name = "Top 5"
  ) %>%
  add_markers(
    data = bottom_points4,
    x = ~county,
    y = ~cardio_hosp_rate_per_10k,
    color = I("blue"),  # Customize color for bottom points
    size = I(10),       # Customize marker size for bottom points
    name = "Bottom 5") %>%
  add_markers(
    data = other_points4,
    x = ~county,
    y = ~cardio_hosp_rate_per_10k,
    color = I("grey"),  # Customize color for other points
    size = I(5),        # Customize marker size for other points
    name = "Other Points"
  )

# Display the plot
cardio_graph
```

TOP 5: <span style="color:red;"> (Montgomery, 200.1), (Greene, 192.3), (Wayne, 191), (Niagara, 182.8), (Sullivan, 181.8) </span>.

BOTTOM 5: <span style="color:blue;"> (Tompskin ,80.4), (Tioga , 84.3), (Chautauqua, 90.2), (Rockland, 104.4), (Essex, 105.8) </span>. 


